Acoustic Scene Classification: \\ Supervised and Unsupervised Approaches using the Scattering Transform

### 2016-06-21 paper/structureScene.tex
call section 3 "scattering transforms"

The scattering transform is a multiscale representation of audio signals which cascades an auditory filterbank and a modulation filterbank, interspersed with complex modulus nonlinearities.
The modulation filterbank may either be performed solely on the time variable or on both time and frequency.
In this section, we present the design of both the temporal scattering transform and the time-frequency scattering transform.

>>>>

\section{Scattering transforms}
The scattering transform is a multiscale representation of audio signals which cascades an auditory filterbank and a modulation filterbank, interspersed with complex modulus nonlinearities.
Depending upon the chosen architecture, the modulation filterbank may either be performed solely over the time variable or on both time and frequency.
In this section, we present both the temporal scattering transform and the time-frequency scattering transform.
